---
title: "CPUE Data Analysis"
output: html_notebook
---

Based upon conversations with Pravin from Stats, use log10 CPUE rather than standardise by estuary/species

Load data and clean up and standardise the winds
```{r}
library(ggplot2)
library(DHARMa)
library(bootpredictlme4)
library(merTools)
library(effects)
library(MuMIn)
library(dplyr)
library(ggeffects)
library(glmmTMB)
library(tweedie)
library(brms)
# Use Log10(CPUE) rather than standardise


# Load Data
mydata <- read.csv("../Data/Full_Data_Modelling_BARRA_by_estuary.csv", header = T) # Full_Data_ModellingV3_by_estuary.csv
# mydata2 <-  read.csv("Full_Data_Modelling.csv", header = T)
# 
# cor.test(mydata$X45_degree_winds, mydata2$X135_degree_winds)
# cor.test(mydata$X135_degree_winds, mydata2$X45_degree_winds)
# cor.test(mydata$X135_degree_winds, mydata2$X135_degree_winds)
# cor.test(mydata$X45_degree_winds, mydata2$X45_degree_winds)
# # NE winds not correlated by SE winds are.....

# Remove Total CPUE
mydata <- subset(mydata, Species != "Total")
mydata <- subset(mydata, Species != "Luderick")

### Standardise Winds
my.df <-  mydata %>% group_by(Species, Estuary) %>% mutate(X45_degree_winds.standardised = as.numeric(scale(X45_degree_winds)),
                           X135_degree_winds.standardised = as.numeric(scale(X135_degree_winds)))

```

Investigate the environmental variation over time and the stability of the CPUE over time
```{r}
head(my.df)

ggplot(my.df, aes(x=Year, y = Drought_Months)) + geom_point() + facet_wrap(~Species)
ggplot(my.df, aes(x=Year, y = Catch/1000, col= Estuary)) + geom_line() + facet_wrap(~Species, scales = "free_y") +
  theme_classic() + ylab("Catch ('000 kg)") +
  theme(axis.title = element_text(face="bold", size=12),
        axis.text.x = element_text(colour = "black", size = 10, angle=45, hjust = 1),
        axis.text.y = element_text(colour = "black", size = 10),
        strip.text = element_text(colour="black", face = "bold", size = 11, hjust=0.5),
        strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size = 1),
        legend.title = element_text(colour="black", size = 12, face = "bold"),
        legend.text = element_text(colour="black", size=10))

ggsave("../plots/Catch by species_time_estuary.png", height = 14.8, width=21, dpi =600, units="cm")

ggplot(my.df, aes(x=Year, y = CPUE, col= Estuary)) + geom_line() + facet_wrap(~Species, scales = "free_y") +
  theme_classic() + ylab("CPUE (kg per day)") +
  theme(axis.title = element_text(face="bold", size=12),
        axis.text.x = element_text(colour = "black", size = 10, angle=45, hjust = 1),
        axis.text.y = element_text(colour = "black", size = 10),
        strip.text = element_text(colour="black", face = "bold", size = 11, hjust=0.5),
        strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size = 1),
        legend.title = element_text(colour="black", size = 12, face = "bold"),
        legend.text = element_text(colour="black", size=10))

ggsave("../plots/CPUE by species_time_estuary.png", height = 14.8, width=21, dpi =600, units="cm")

# the next two suggest my scaling of the winds was not good enough.
ggplot(my.df, aes(x=Year, y = X45_degree_winds.standardised, col= Estuary)) + geom_line() + facet_wrap(~Species) +
  theme_classic() + ylab("Standardised Upwelling\nFavourable Winds") +
  theme(axis.title = element_text(face="bold", size=12),
        axis.text.x = element_text(colour = "black", size = 10, angle=45, hjust = 1),
        axis.text.y = element_text(colour = "black", size = 10),
        strip.text = element_text(colour="black", face = "bold", size = 11, hjust=0.5),
        strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size = 1),
        legend.title = element_text(colour="black", size = 12, face = "bold"),
        legend.text = element_text(colour="black", size=10))

ggsave("../plots/Upwelling Winds by species_time_estuary.png", height = 14.8, width=21, dpi =600, units="cm")

ggplot(my.df, aes(x=Year, y = X135_degree_winds.standardised, col= Estuary)) + geom_line() + facet_wrap(~Species)+
  theme_classic() + ylab("Standardised Downwelling\nFavourable Winds") +
  theme(axis.title = element_text(face="bold", size=12),
        axis.text.x = element_text(colour = "black", size = 10, angle=45, hjust = 1),
        axis.text.y = element_text(colour = "black", size = 10),
        strip.text = element_text(colour="black", face = "bold", size = 11, hjust=0.5),
        strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size = 1),
        legend.title = element_text(colour="black", size = 12, face = "bold"),
        legend.text = element_text(colour="black", size=10))#, scales = "free_y")
ggsave("../plots/Downwelling Winds by species_time_estuary.png", height = 14.8, width=21, dpi =600, units="cm")


ggplot(my.df, aes(x=Year, y = Effort_days, col= Estuary)) + geom_line()+ #+ facet_wrap(~Species)+
  theme_classic() + ylab("Effort (Fishing Days)") +
  scale_y_log10()+
  theme(axis.title = element_text(face="bold", size=12),
        axis.text.x = element_text(colour = "black", size = 10, angle=45, hjust = 1),
        axis.text.y = element_text(colour = "black", size = 10),
        strip.text = element_text(colour="black", face = "bold", size = 11, hjust=0.5),
        strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill=NA, size = 1),
        legend.title = element_text(colour="black", size = 12, face = "bold"),
        legend.text = element_text(colour="black", size=10))#, scales = "free_y")
ggsave("../plots/Fishing Effort over time.png", height = 14.8, width=21, dpi =600, units="cm")

```



Do full model for all species

Bayesian Model
```{r}
library(brms)
library(tidyverse)

my.df2 <- my.df %>% drop_na(X135_degree_winds.standardised, X45_degree_winds.standardised)

m7a <- brm(CPUE ~ poly(X135_degree_winds.standardised, degree = 2) + 
             poly(X45_degree_winds.standardised, degree = 2) +
             X135_degree_winds.standardised:X45_degree_winds.standardised+
             Estuary_Type *Drought_Months + Species + (Species|Estuary),
           data = my.df2, iter = 10000, seed = 1234)
saveRDS(m7a, "../Data/Fisheries Data/Lag Models/CPUE Multi_species brms model CPUE no lag.rds")
m7a <- readRDS("../Data/Fisheries Data/Lag Models/CPUE Multi_species brms model CPUE no lag.rds")

```

```{r}
table(my.df2$Species, my.df2$Year)
#table(my.df2$Estuary, my.df2$Estuary_Type)
```


Check model
```{r}
#plot(m7a)
summary(m7a)
ranef(m7a)
fixef(m7a)
brms::prior_summary(m7a)
mcmc_plot(m7a)
bayes_R2(m7a)
performance::r2_bayes(m7a)
```
marginal effects
```{r}
#plot(conditional_effects(m7a))

#plot(ggpredict(m7a, terms = "X45_degree_winds.standardised [all]"))

M_dat <- ggpredict(m7a, terms = "X45_degree_winds.standardised [all]")
M_dat$Term <- "Upwelling \nFavourable Winds"

M_plot <- ggplot(M_dat, aes(x, predicted/1000))+
  geom_line() + xlab("Upwelling\nFavourable Winds")+
  geom_ribbon(aes(ymin = conf.low/1000, ymax = conf.high/1000), alpha = .1) +
  theme_classic() + theme(axis.text  = element_text(colour="black", size = 12), 
                          axis.title = element_text(face="bold", colour="black", size = 14),
                          axis.ticks = element_line(colour="black"),
                          strip.text = element_text(colour="black", face = "bold", size = 13),
                          strip.background = element_blank(),
                          strip.placement = "outside",
                          #legend.justification=c(1,0), legend.position="right",
                          panel.border = element_rect(colour = "black", fill=NA, size = 1),
                          title = element_text(size=12, face = "bold"))+
  ylab("Predicted CPUE (kg / day)")# +
  #ggtitle("c) Mullet")
M_plot  
ggsave("../plots/CPUE Multispecies.png", dpi = 600, width = 10, height = 12, units = "cm")
```

Get co-eff outputs
```{r}
library(tidybayes)
library(tidyverse)
get_variables(m7a)

m7a %>%
  spread_draws(b_Intercept,b_polyX135_degree_winds.standardiseddegreeEQ21,
               b_polyX135_degree_winds.standardiseddegreeEQ22, b_polyX45_degree_winds.standardiseddegreeEQ21,
               b_polyX45_degree_winds.standardiseddegreeEQ22, b_Estuary_TypeBarrierRiver,
               b_Estuary_TypeDrownedRiverValley, b_Drought_Months,
               b_SpeciesFlathead, b_SpeciesMullet, b_SpeciesWhiting, 
               `b_X135_degree_winds.standardised:X45_degree_winds.standardised`,
               `b_Estuary_TypeBarrierRiver:Drought_Months`, `b_Estuary_TypeDrownedRiverValley:Drought_Months`) %>%
  rename("Intercept" = b_Intercept, "Up" = b_polyX45_degree_winds.standardiseddegreeEQ21,
        "Up (quadratic)"  = b_polyX45_degree_winds.standardiseddegreeEQ22, "Drought" = b_Drought_Months,
         "Down" = b_polyX135_degree_winds.standardiseddegreeEQ21, "Down (quadratic)" = b_polyX135_degree_winds.standardiseddegreeEQ22,
         "Down * Up" = `b_X135_degree_winds.standardised:X45_degree_winds.standardised`,
        "Est Type (Barrier River)" = b_Estuary_TypeBarrierRiver, "Est Type (Drowned River Valley)" = b_Estuary_TypeDrownedRiverValley,
        "Est Type (Barrier River) * Drought" = `b_Estuary_TypeBarrierRiver:Drought_Months`,
        "Est Type (Drowned River Valley) * Drought" = `b_Estuary_TypeDrownedRiverValley:Drought_Months`,
        "Species: Flathead" = b_SpeciesFlathead, "Species: Mullet" = b_SpeciesMullet, "Species: Whiting" = b_SpeciesWhiting) %>%
  tidyr::pivot_longer(cols = c(4:17), names_to = "Parameter") %>%
  #median_qi() %>%
  ggplot(aes(x = value, y = Parameter)) +
  stat_halfeye(normalize = "groups") + geom_vline(xintercept =0 , col = "red", lty = 2) +
  xlab("Estimate")+
  theme_classic() + theme(axis.text = element_text(colour="black"),
                          axis.title = element_text(face = "bold"))# +
  #scale_y_continuous(trans = ggallin::ssqrt_trans, breaks = c(-20, -10, -1,1,10,20))
ggsave("../plots/CPUE mulitspecies Estimate plots.png", dpi = 600, height = 12, width = 18, units= "cm")
```


```{r}
# Which ones are actually important effects/interactions
m7a %>%
  gather_draws(b_Intercept,b_polyX135_degree_winds.standardiseddegreeEQ21,
               b_polyX135_degree_winds.standardiseddegreeEQ22, b_polyX45_degree_winds.standardiseddegreeEQ21,
               b_polyX45_degree_winds.standardiseddegreeEQ22, b_Estuary_TypeBarrierRiver,
               b_Estuary_TypeDrownedRiverValley, b_Drought_Months,
               b_SpeciesFlathead, b_SpeciesMullet, b_SpeciesWhiting, 
               `b_X135_degree_winds.standardised:X45_degree_winds.standardised`,
               `b_Estuary_TypeBarrierRiver:Drought_Months`, `b_Estuary_TypeDrownedRiverValley:Drought_Months`) %>%
  median_qi() #%>%
```


Model checks
```{r}
my.df2 %>%
  add_residual_draws(m7a) %>%
  ggplot(aes(x = .row, y = .residual)) +
  stat_pointinterval()
```


```{r}
my.df2 %>%
  add_residual_draws(m7a) %>%
  median_qi() %>%
  ggplot(aes(sample = .residual)) +
  geom_qq() +
  geom_qq_line()

my.df2 %>%
  add_predicted_draws(m7a) %>%
  summarise(
    p_residual = mean(.prediction < CPUE),
    z_residual = qnorm(p_residual)
  ) %>%
  ggplot(aes(sample = z_residual)) +
  geom_qq() +
  geom_abline()
```






Save model checking plots - These were combined manually in Inkscape later
```{r}
### Residual plots
m6.residual <- data.frame(residuals(m7a,summary = TRUE))
m6.fitted <- data.frame(fitted(m7a, summary = TRUE))
m6.predicted <- data.frame(predict(m7a,summary = TRUE))
coef(m7a)

m6.re <- cbind(m6.residual,m6.fitted,m6.predicted)
colnames(m6.re) <- c("Residual","residual.Error","residual.Q2.5","residual.Q97.5",
                     "Fitted","fitted.Error","fitted.Q2.5","fitted.Q97.5",
                     "Predicted","predicted.Error","predicted.Q2.5","predicted.Q97.5")
m6.re <- cbind(my.df2,m6.re)

# Basic version of observed vs fitted values#
ggplot(m6.re, aes(x = Fitted, y = CPUE)) + 
  geom_point() + 
  geom_smooth(method = 'gam', formula = y ~ s(x, bs = 'cs', k = 5), se = FALSE, size = 1.25,colour="black") +
  xlab('Fitted age-0+ Atlantic salmon density') +
  ylab('Observed age-0+ Atlantic salmon density')+ theme_classic()+
  theme(axis.title = element_text(size=12, face = "bold"),
        axis.text = element_text(size = 10, colour = "black")) #+
#style

#ggsave("Figure_Sal_observed vs fitted.png",width = 17, height = 9)


#Density histogram of residuals
hist_p <- ggplot(m6.re, aes(x = Residual)) + 
  geom_histogram(aes(y = ..density..), bins = 15, fill = 'grey', colour = 'black') + 
  geom_line(aes(y = ..density..), stat = 'density') +
  xlab('Residual') + theme_classic()+
  ylab('Density') +
  theme(axis.title = element_text(size=12, face = "bold"),
        axis.text = element_text(size = 10, colour = "black"))#+
#style
hist_p

#ggsave("Figure_Sal_density histogram of residuals.png",width = 17, height = 9)

 #QQ plot#
 QQ_p <- my.df2 %>%
   add_residual_draws(m7a) %>%
   median_qi() %>%
   ggplot(aes(sample = .residual)) +
   geom_qq() +
   geom_qq_line() + theme_classic()+
   theme(axis.title = element_text(size=12, face = "bold"),
        axis.text = element_text(size = 10, colour = "black"))+
   xlab('Theoretical quantiles') +
   ylab('Sample quantiles')# +
 #style
 QQ_p


qq_plot <- my.df2 %>%
  add_predicted_draws(m7a) %>%
  summarise(
    p_residual = mean(.prediction < CPUE),
    z_residual = qnorm(p_residual)
  ) %>%
  ggplot(aes(sample = z_residual)) +
  geom_qq() + ylab("Sample") + xlab("Theoretical")+
  geom_abline() + theme_classic() + theme_classic()+
  theme(axis.title = element_text(size=12, face = "bold"),
        axis.text = element_text(size = 10, colour = "black"))


#ggsave("Figure_Sal_QQ_Plot.png",width = 17, height = 9)

#Residuals vs fitted
Resid_p <- ggplot(m6.re, aes(x = Fitted, y = Residual)) + 
  geom_point() + 
  geom_smooth(method = 'gam', formula = y ~ s(x, bs = 'cs', k = 5), se = FALSE, size = 1.25,colour="black") +
  xlab('Fitted value') +
  ylab("Pearson's residuals") +
  theme(axis.title.x=element_text(vjust=1.8))+ theme_classic()+
  theme(axis.title = element_text(size=12, face = "bold"),
        axis.text = element_text(size = 10, colour = "black")) #+
#style
Resid_p
#ggsave("Figure_Sal_residuals vs fitted.png",width = 17, height = 9)

#acf#
rs <- data.frame('r' = resid(m7a),'f.' = fitted(m7a))

require(ggfortify)
acf_p <- autoplot(acf(rs$r.Estimate)) + 
  ylab("Autocorrelation function") +
  ggtitle("") + 
  theme(axis.title.x=element_text(vjust=1.8)) +
  geom_hline(yintercept = 0)+ theme_classic()+
  theme(axis.title = element_text(size=12, face = "bold"),
        axis.text = element_text(size = 10, colour = "black")) #+
#style
acf_p

library(gridExtra)

ggsave("../Plots/CPUE_ModelDiagnostics.png", arrangeGrob(hist_p, QQ_p, Resid_p, acf_p, ncol = 2,nrow = 2),width = 9.5, height = 7.5)
dev.off()
```




```{r}
plot(ggeffect(m7a, terms = "X45_degree_winds.standardised [all]"))
plot(ggeffect(m7a, terms = "X135_degree_winds.standardised [all]"))
plot(ggeffect(m7a, terms = "Drought_Months [all]"))
```
Heatmap making for interaction plot (Run from here) - Very slow if standard error included (was run on HPC to get SE)
```{r message=FALSE}
nums <- seq(-2,2, by = 0.05)
heat_dataM <- data.frame("X135_degree_winds.standardised" = rep(0,81*81), # makes empty dataframe ready for values
                         "X45_degree_winds.standardised" =  rep(0,81*81),
                         "Catch" =  rep(0,81*81))
Nn <- 1
# loop for NE
for (i in 1:length(nums)){
  for (j in 1:length(nums)){
    pred_map <- data.frame("X45_degree_winds.standardised" = nums[i],
                           "X135_degree_winds.standardised" = nums[j],
                           "Drought_Months" = mean(my.df$Drought_Months),
                           "Estuary_Type" = "Drowned River Valley",
                           "Estuary" = "Hawkesbury River",
                           "Species" = "Bream",
                           "Effort_days" = mean(my.df$Effort_days))
    PredX <- predict(m7, newdata = pred_map, type = "response", se.fit = F)
    heat_dataM$Southeast.Winds[Nn] <- pred_map$X135_degree_winds.standardised[1]
    heat_dataM$Northeast.Winds[Nn] <- pred_map$X45_degree_winds.standardised[1]
    heat_dataM$Abundance[Nn] <- PredX#$fit
    #print(paste("This is line ", Nn, " out of 6561"))
    Nn <- Nn + 1
  }
}

pH <- ggplot(heat_dataM, aes(x = Southeast.Winds,y = Northeast.Winds)) + geom_tile(aes(fill = Abundance)) +
  geom_contour(col="white", aes(z = Abundance)) +#, binwidth = 0.002
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  #scale_fill_gradient(low = "blue", high = "red") +
  theme_classic() +
  viridis::scale_fill_viridis(option = "magma", name="Predicted Catch") + # or geom_raster()
  xlab("Downwelling \nFavourable Winds") + ylab("Upwelling \nFavourable Winds") +
  theme(axis.title.x = element_text(face="bold", colour="black", size = 15),
        axis.text.x  = element_text(colour="black", size = 14),
        axis.title.y = element_text(face="bold", colour="black", size = 15),
        axis.text.y  = element_text(colour="black", size = 14),
        axis.ticks = element_line(colour="black"),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=10),
        legend.position = "bottom")

pH

write.csv(heat_dataM, "../Data/All Species heamap prediction data.csv", row.names = F)

```

