---
title: "CPUE Data Analysis"
output: html_notebook
---

Based upon conversations with Pravin from Stats, use log10 CPUE rather than standardise by estuary/species

Load data and clean up and standardise the winds
```{r}
library(ggplot2)
library(DHARMa)
library(bootpredictlme4)
library(merTools)
library(effects)
library(MuMIn)
library(dplyr)
library(ggeffects)
library(glmmTMB)
library(tweedie)
# Use Log10(CPUE) rather than standardise


# Load Data
mydata <- read.csv("../Data/Full_Data_Modelling_BARRA_by_estuary.csv", header = T) # Full_Data_ModellingV3_by_estuary.csv
# mydata2 <-  read.csv("Full_Data_Modelling.csv", header = T)
# 
# cor.test(mydata$X45_degree_winds, mydata2$X135_degree_winds)
# cor.test(mydata$X135_degree_winds, mydata2$X45_degree_winds)
# cor.test(mydata$X135_degree_winds, mydata2$X135_degree_winds)
# cor.test(mydata$X45_degree_winds, mydata2$X45_degree_winds)
# # NE winds not correlated by SE winds are.....

# Remove Total CPUE
mydata <- subset(mydata, Species != "Total")

### Standardise Winds
my.df <-  mydata %>% group_by(Species) %>% mutate(X45_degree_winds.standardised = as.numeric(scale(X45_degree_winds)),
                           X135_degree_winds.standardised = as.numeric(scale(X135_degree_winds)))

```

Investigate the environmental variation over time and the stability of the CPUE over time
```{r}
head(my.df)

ggplot(my.df, aes(x=Year, y = Drought_Months)) + geom_point() + facet_wrap(~Species)
ggplot(my.df, aes(x=Year, y = CPUE, col= Estuary)) + geom_line() + facet_wrap(~Species, scales = "free_y")

# the next two suggest my scaling of the winds was not good enough.
ggplot(my.df, aes(x=Year, y = X45_degree_winds.standardised, col= Estuary)) + geom_line() + facet_wrap(~Species)#, scales = "free_y")
ggplot(my.df, aes(x=Year, y = X135_degree_winds.standardised, col= Estuary)) + geom_line() + facet_wrap(~Species)#, scales = "free_y")


```



Do full model for all species

```{r}
m7 <- glmmTMB(Catch ~ poly(X135_degree_winds.standardised, degree = 2) + 
       poly(X45_degree_winds.standardised, degree = 2) +
       X135_degree_winds.standardised:X45_degree_winds.standardised+
        Estuary_Type *Drought_Months + Species + (Species|Estuary), family = Gamma(link="log"),
       data = my.df, offset = log10(Effort_days))
AIC(m7) # -38.18
performance::r2(m7) # 0.08

simulationOutput <- simulateResiduals(fittedModel = m7, n = 250)
plot(simulationOutput)
hist(residuals(m7))

car::Anova(m7)
summary(m7)

total_Summary <- broom.mixed::tidy(m7)
total_Summary
write.csv(total_Summary, "../Data/All Species Summary Table.csv", row.names = F)

```

Save model checking plots - These were combined manually in Inkscape later
```{r}
#png("../plots/Model checks/Mulitspecies model 1.png", width = 21, height = 14.8, units = "cm", res = 600)
#plot(m7)
#dev.off()

#png("../plots/Model checks/Mulitspecies model 2.png", width = 21, height = 14.8, units = "cm", res = 600)
#hist(resid(m7))
#dev.off()

#png("../plots/Model checks/Mulitspecies model 3.png", width = 21, height = 14.8, units = "cm", res = 600)
#lattice::qqmath(m7)
#dev.off()
```




```{r}
plot(ggeffect(m7, terms = "X45_degree_winds.standardised [all]"))
plot(ggeffect(m7, terms = "X135_degree_winds.standardised [all]"))
plot(ggeffect(m7, terms = "Drought_Months [all]"))
```
Heatmap making for interaction plot (Run from here) - Very slow if standard error included (was run on HPC to get SE)
```{r message=FALSE}
nums <- seq(-2,2, by = 0.05)
heat_dataM <- data.frame("X135_degree_winds.standardised" = rep(0,81*81), # makes empty dataframe ready for values
                         "X45_degree_winds.standardised" =  rep(0,81*81), 
                         "Catch" =  rep(0,81*81))
Nn <- 1
# loop for NE
for (i in 1:length(nums)){
  for (j in 1:length(nums)){
    pred_map <- data.frame("X45_degree_winds.standardised" = nums[i],
                           "X135_degree_winds.standardised" = nums[j],
                           "Drought_Months" = mean(my.df$Drought_Months),
                           "Estuary_Type" = "Drowned River Valley",
                           "Estuary" = "Hawkesbury River",
                           "Species" = "Bream",
                           "Effort_days" = mean(my.df$Effort_days))
    PredX <- predict(m7, newdata = pred_map, type = "response", se.fit = F)
    heat_dataM$Southeast.Winds[Nn] <- pred_map$X135_degree_winds.standardised[1]
    heat_dataM$Northeast.Winds[Nn] <- pred_map$X45_degree_winds.standardised[1]
    heat_dataM$Abundance[Nn] <- PredX#$fit
    #print(paste("This is line ", Nn, " out of 6561"))
    Nn <- Nn + 1
  }
}

pH <- ggplot(heat_dataM, aes(x = Southeast.Winds,y = Northeast.Winds)) + geom_tile(aes(fill = Abundance)) +
  geom_contour(col="white", aes(z = Abundance)) +#, binwidth = 0.002
  scale_x_continuous(expand = c(0,0)) + 
  scale_y_continuous(expand = c(0,0)) +
  #scale_fill_gradient(low = "blue", high = "red") + 
  theme_classic() + 
  viridis::scale_fill_viridis(option = "magma", name="Predicted Catch") + # or geom_raster()
  xlab("Downwelling \nFavourable Winds") + ylab("Upwelling \nFavourable Winds") +
  theme(axis.title.x = element_text(face="bold", colour="black", size = 15),
        axis.text.x  = element_text(colour="black", size = 14), 
        axis.title.y = element_text(face="bold", colour="black", size = 15),
        axis.text.y  = element_text(colour="black", size = 14),
        axis.ticks = element_line(colour="black"),
        legend.title = element_text(colour="black", size=12, face="bold"),
        legend.text = element_text(colour="black", size=10),
        legend.position = "bottom") 

pH

write.csv(heat_dataM, "../Data/All Species heamap prediction data.csv", row.names = F)

```



Now for some species specific Models
Bream First
Prepare Data
```{r}
bream <- subset(my.df, Species == "Bream")

```

Model
```{r}
m1 <- glmmTMB(Catch ~ poly(X135_degree_winds.standardised, degree = 2) + 
       poly(X45_degree_winds.standardised, degree = 2) +
       X135_degree_winds.standardised:X45_degree_winds.standardised+
        Estuary_Type *Drought_Months + (1|Estuary) , family = Gamma(link="log"),
       data = bream, offset = log10(Effort_days),
        legend.position = "bottom")
performance::r2(m1) # 0.266
AIC(m1) # 43.17
```

Check assumptions
```{r}
simulationOutput <- simulateResiduals(fittedModel = m1, n = 250)
plot(simulationOutput)

# histograms
hist(simulationOutput$fittedResiduals)
```

Model checking plots - note these were combined in Inkscape manually later
```{r}
#png("../plots/Model checks/Bream model 1.png", width = 21, height = 14.8, units = "cm", res = 600)
#plot(m1)
#dev.off()

#png("../plots/Model checks/Bream model 2.png", width = 21, height = 14.8, units = "cm", res = 600)
#hist(resid(m1))
#dev.off()

#png("../plots/Model checks/Bream model 3.png", width = 21, height = 14.8, units = "cm", res = 600)
#lattice::qqmath(m1)
#dev.off()
```


Check significance
```{r}
car::Anova(m1)

summary(m1)

bream_Summary <- broom.mixed::tidy(m1)
bream_Summary
write.csv(bream_Summary, "../Data/Bream Summary Table.csv", row.names = F)

```

```{r}
plot(ggeffect(m1, terms = "X45_degree_winds.standardised [all]"))
plot(ggeffect(m1, terms = "X135_degree_winds.standardised [all]"))
plot(ggeffect(m1, terms = "Drought_Months [all]"))
```
Heatmap making for interaction plot (Run from here) - Very slow if standard error included (was run on HPC to get SE)
```{r message=FALSE}
nums <- seq(-2,2, by = 0.05)
heat_dataBream <- data.frame("X135_degree_winds.standardised" = rep(0,81*81), # makes empty dataframe ready for values
                         "X45_degree_winds.standardised" =  rep(0,81*81), 
                         "Catch" =  rep(0,81*81))
Nn <- 1
# loop for NE
for (i in 1:length(nums)){
  for (j in 1:length(nums)){
    pred_map <- data.frame("X45_degree_winds.standardised" = nums[i],
                           "X135_degree_winds.standardised" = nums[j],
                           "Drought_Months" = mean(my.df$Drought_Months),
                           "Estuary_Type" = "Drowned River Valley",
                           "Estuary" = "Hawkesbury River",
                           "Effort_days" = mean(my.df$Effort_days))
    PredX <- predict(m1, newdata = pred_map, type = "response", se.fit = F)
    heat_dataBream$Southeast.Winds[Nn] <- pred_map$X135_degree_winds.standardised[1]
    heat_dataBream$Northeast.Winds[Nn] <- pred_map$X45_degree_winds.standardised[1]
    heat_dataBream$Abundance[Nn] <- PredX#$fit
    #print(paste("This is line ", Nn, " out of 6561"))
    Nn <- Nn + 1
  }
}

pB <- ggplot(heat_dataBream, aes(x = Southeast.Winds,y = Northeast.Winds)) + geom_tile(aes(fill = Abundance)) +
  geom_contour(col="white", aes(z = Abundance)) +#, binwidth = 0.002
  scale_x_continuous(expand = c(0,0)) + 
  scale_y_continuous(expand = c(0,0)) +
  #scale_fill_gradient(low = "blue", high = "red") + 
  theme_classic() + 
  viridis::scale_fill_viridis(option = "magma", name="Predicted Catch") + # or geom_raster()
  xlab("Downwelling \nFavourable Winds") + ylab("Upwelling \nFavourable Winds") +
  theme(axis.title.x = element_text(face="bold", colour="black", size = 15),
        axis.text.x  = element_text(colour="black", size = 14), 
        axis.title.y = element_text(face="bold", colour="black", size = 15),
        axis.text.y  = element_text(colour="black", size = 14),
        axis.ticks = element_line(colour="black"),
        legend.title = element_blank(),
        legend.text = element_text(colour="black", size=10),
        legend.position = "bottom") 

pB

write.csv(heat_dataBream, "../Data/Bream heamap prediction data.csv", row.names = F)

```


##Now Mullet##
Prepare Data
```{r}
mullet <- subset(my.df, Species == "Mullet")

p2 <- ggplot(mullet, aes(x = X135_degree_winds.standardised,y = X45_degree_winds.standardised, size = log10(CPUE))) + geom_point(alpha = 0.1) +
  theme_classic() + labs(title = "CPUE by lagged Winds")
p2
```

Model
```{r}
m2 <- glmmTMB(Catch ~ poly(X135_degree_winds.standardised, degree = 2) + 
       poly(X45_degree_winds.standardised, degree = 2) +
       X135_degree_winds.standardised:X45_degree_winds.standardised+
        Estuary_Type *Drought_Months + (1|Estuary) , family = Gamma(link="log"),
       data = mullet, offset = log10(Effort_days))
performance::r2(m2) # 0.147
AIC(m2) # -22.726
```

Check assumptions
```{r}
simulationOutput <- simulateResiduals(fittedModel = m2, n = 250)
plot(simulationOutput)

# histograms
hist(simulationOutput$fittedResiduals)
```

```{r}
#png("../plots/Model checks/Mullet model 1.png", width = 21, height = 14.8, units = "cm", res = 600)
#plot(m2)
#dev.off()

#png("../plots/Model checks/Mullet model 2.png", width = 21, height = 14.8, units = "cm", res = 600)
#hist(resid(m2))
#dev.off()

#png("../plots/Model checks/Mullet model 3.png", width = 21, height = 14.8, units = "cm", res = 600)
#lattice::qqmath(m2)
#dev.off()
```


Check significance
```{r}
car::Anova(m2)

summary(m2)
mullet_Summary <- broom.mixed::tidy(m2)
mullet_Summary
write.csv(mullet_Summary, "../Data/Mullet Summary Table.csv", row.names = F)

```
Therefore wind is not important for mullet?

```{r}
plot(allEffects(m2))
```

```{r}
plot(ggeffect(m2, terms = "X45_degree_winds.standardised [all]"))
plot(ggeffect(m2, terms = "X135_degree_winds.standardised [all]"))
plot(ggeffect(m2, terms = "Drought_Months [all]"))
```


```{r}
nums <- seq(-2,2, by = 0.05)
heat_dataMullet <- data.frame("X135_degree_winds.standardised" = rep(0,81*81), # makes empty dataframe ready for values
                         "X45_degree_winds.standardised" =  rep(0,81*81), 
                         "Catch" =  rep(0,81*81))
Nn <- 1
# loop for NE
for (i in 1:length(nums)){
  for (j in 1:length(nums)){
    pred_map <- data.frame("X45_degree_winds.standardised" = nums[i],
                           "X135_degree_winds.standardised" = nums[j],
                           "Drought_Months" = mean(my.df$Drought_Months),
                           "Estuary_Type" = "Drowned River Valley",
                           "Estuary" = "Hawkesbury River",
                           "Effort_days" = mean(my.df$Effort_days))
    PredX <- predict(m2, newdata = pred_map, type = "response", se.fit = F)
    heat_dataMullet$Southeast.Winds[Nn] <- pred_map$X135_degree_winds.standardised[1]
    heat_dataMullet$Northeast.Winds[Nn] <- pred_map$X45_degree_winds.standardised[1]
    heat_dataMullet$Abundance[Nn] <- PredX#$fit
    #print(paste("This is line ", Nn, " out of 6561"))
    Nn <- Nn + 1
  }
}

pM <- ggplot(heat_dataMullet, aes(x = Southeast.Winds,y = Northeast.Winds)) + geom_tile(aes(fill = Abundance)) +
  geom_contour(col="white", aes(z = Abundance)) +#, binwidth = 0.002
  scale_x_continuous(expand = c(0,0)) + 
  scale_y_continuous(expand = c(0,0)) +
  #scale_fill_gradient(low = "blue", high = "red") + 
  theme_classic() + 
  viridis::scale_fill_viridis(option = "magma", name="Predicted Catch") + # or geom_raster()
  xlab("Downwelling \nFavourable Winds") + ylab("Upwelling \nFavourable Winds") +
  theme(axis.title.x = element_text(face="bold", colour="black", size = 15),
        axis.text.x  = element_text(colour="black", size = 14), 
        axis.title.y = element_text(face="bold", colour="black", size = 15),
        axis.text.y  = element_text(colour="black", size = 14),
        axis.ticks = element_line(colour="black"),
        legend.title = element_blank(),
        legend.text = element_text(colour="black", size=10),
        legend.position = "bottom") 

pM

write.csv(heat_dataMullet, "../Data/Mullet heamap prediction data.csv", row.names = F)

```


##Now Whiting##
Prepare Data
```{r}
whiting <- subset(my.df, Species == "Whiting")

#m1 <- lmer(CPUE.standardised ~ X135_degree_winds.standardised * X45_degree_winds.standardised + 
#           Estuary_Type + Drought_Months + (1|Estuary), data = bream)
#AIC(m1) #215.42

p3 <- ggplot(whiting, aes(x = X135_degree_winds.standardised,y = X45_degree_winds.standardised, size = log10(CPUE))) + geom_point(alpha = 0.1) +
  theme_classic() + labs(title = "CPUE by lagged Winds")
p3
```

Model
```{r}
m3 <- glmmTMB(Catch ~ poly(X135_degree_winds.standardised, degree = 2) + 
       poly(X45_degree_winds.standardised, degree = 2) +
       X135_degree_winds.standardised:X45_degree_winds.standardised+
        Estuary_Type *Drought_Months + (1|Estuary) , family = Gamma(link="log"),
       data = whiting, offset = log10(Effort_days))
performance::r2(m3) # 0.127
AIC(m3) # 64.26
```

Check assumptions
```{r}
simulationOutput <- simulateResiduals(fittedModel = m3, n = 250)
plot(simulationOutput)

# histograms
hist(simulationOutput$fittedResiduals)
```

```{r}
#png("../plots/Model checks/Whiting model 1.png", width = 21, height = 14.8, units = "cm", res = 600)
#plot(m3)
#dev.off()

#png("../plots/Model checks/Whiting model 2.png", width = 21, height = 14.8, units = "cm", res = 600)
#hist(resid(m3))
#dev.off()

#png("../plots/Model checks/Whiting model 3.png", width = 21, height = 14.8, units = "cm", res = 600)
#lattice::qqmath(m3)
#dev.off()
```


Check significance
```{r}
car::Anova(m3)
summary(m3)
whiting_Summary <- broom.mixed::tidy(m3)
whiting_Summary
write.csv(whiting_Summary, "../Data/Whiting Summary Table.csv", row.names = F)

```
Therefore wind is not important for whiting?

```{r}
plot(ggeffect(m3, terms = "X45_degree_winds.standardised [all]"))
plot(ggeffect(m3, terms = "X135_degree_winds.standardised [all]"))
plot(ggeffect(m3, terms = "Drought_Months [all]"))
```
```{r}
nums <- seq(-2,2, by = 0.05)
heat_dataWhiting <- data.frame("X135_degree_winds.standardised" = rep(0,81*81), # makes empty dataframe ready for values
                         "X45_degree_winds.standardised" =  rep(0,81*81), 
                         "Catch" =  rep(0,81*81))
Nn <- 1
# loop for NE
for (i in 1:length(nums)){
  for (j in 1:length(nums)){
    pred_map <- data.frame("X45_degree_winds.standardised" = nums[i],
                           "X135_degree_winds.standardised" = nums[j],
                           "Drought_Months" = mean(my.df$Drought_Months),
                           "Estuary_Type" = "Drowned River Valley",
                           "Estuary" = "Hawkesbury River",
                           "Effort_days" = mean(my.df$Effort_days))
    PredX <- predict(m3, newdata = pred_map, type = "response", se.fit = F)
    heat_dataWhiting$Southeast.Winds[Nn] <- pred_map$X135_degree_winds.standardised[1]
    heat_dataWhiting$Northeast.Winds[Nn] <- pred_map$X45_degree_winds.standardised[1]
    heat_dataWhiting$Abundance[Nn] <- PredX#$fit
    #print(paste("This is line ", Nn, " out of 6561"))
    Nn <- Nn + 1
  }
}

pW <- ggplot(heat_dataWhiting, aes(x = Southeast.Winds,y = Northeast.Winds)) + geom_tile(aes(fill = Abundance)) +
  geom_contour(col="white", aes(z = Abundance)) +#, binwidth = 0.002
  scale_x_continuous(expand = c(0,0)) + 
  scale_y_continuous(expand = c(0,0)) +
  #scale_fill_gradient(low = "blue", high = "red") + 
  theme_classic() + 
  viridis::scale_fill_viridis(option = "magma", name="Predicted Catch") + # or geom_raster()
  xlab("Downwelling \nFavourable Winds") + ylab("Upwelling \nFavourable Winds") +
  theme(axis.title.x = element_text(face="bold", colour="black", size = 15),
        axis.text.x  = element_text(colour="black", size = 14), 
        axis.title.y = element_text(face="bold", colour="black", size = 15),
        axis.text.y  = element_text(colour="black", size = 14),
        axis.ticks = element_line(colour="black"),
        legend.title = element_blank(),
        legend.text = element_text(colour="black", size=10),
        legend.position = "bottom") 

pW

write.csv(heat_dataWhiting, "../Data/Whiting heamap prediction data.csv", row.names = F)

```



##Now Luderick##
Prepare Data
```{r}
luderick <- subset(my.df, Species == "Luderick")

#m1 <- lmer(CPUE.standardised ~ X135_degree_winds.standardised * X45_degree_winds.standardised + 
#           Estuary_Type + Drought_Months + (1|Estuary), data = bream)
#AIC(m1) #215.42

p4 <- ggplot(luderick, aes(x = X135_degree_winds.standardised,y = X45_degree_winds.standardised, size = log10(CPUE))) + geom_point(alpha = 0.1) +
  theme_classic() + labs(title = "CPUE by lagged Winds")
p4
```

Model
```{r}
m4 <- glmmTMB(Catch ~ poly(X135_degree_winds.standardised, degree = 2) + 
       poly(X45_degree_winds.standardised, degree = 2) +
       X135_degree_winds.standardised:X45_degree_winds.standardised+
        Estuary_Type *Drought_Months + (1|Estuary) , Gamma(link="log"),
       data = luderick, offset = log10(Effort_days))
performance::r2(m4) # 0.127
AIC(m4) # 64.26
```

Check assumptions
```{r}
simulationOutput <- simulateResiduals(fittedModel = m4, n = 250)
plot(simulationOutput)

# histograms
hist(simulationOutput$fittedResiduals)
```

```{r}
#png("../plots/Model checks/Luderick model 1.png", width = 21, height = 14.8, units = "cm", res = 600)
#plot(m4)
#dev.off()

#png("../plots/Model checks/Luderick model 2.png", width = 21, height = 14.8, units = "cm", res = 600)
#hist(resid(m4))
#dev.off()

#png("../plots/Model checks/Luderick model 3.png", width = 21, height = 14.8, units = "cm", res = 600)
#lattice::qqmath(m4)
#dev.off()
```


Check significance
```{r}
car::Anova(m4)
summary(m4)
luderick_Summary <- broom.mixed::tidy(m4)
luderick_Summary
write.csv(luderick_Summary, "../Data/Luderick Summary Table.csv", row.names = F)
```
Therefore wind is not important for luderick?

```{r}
plot(ggeffect(m4, terms = "X45_degree_winds.standardised [all]"))
plot(ggeffect(m4, terms = "X135_degree_winds.standardised [all]"))
plot(ggeffect(m4, terms = "Drought_Months [all]"))
```

```{r}
nums <- seq(-2,2, by = 0.05)
heat_dataLuderick <- data.frame("X135_degree_winds.standardised" = rep(0,81*81), # makes empty dataframe ready for values
                         "X45_degree_winds.standardised" =  rep(0,81*81), 
                         "Catch" =  rep(0,81*81))
Nn <- 1
# loop for NE
for (i in 1:length(nums)){
  for (j in 1:length(nums)){
    pred_map <- data.frame("X45_degree_winds.standardised" = nums[i],
                           "X135_degree_winds.standardised" = nums[j],
                           "Drought_Months" = mean(my.df$Drought_Months),
                           "Estuary_Type" = "Drowned River Valley",
                           "Estuary" = "Hawkesbury River",
                           "Effort_days" = mean(my.df$Effort_days))
    PredX <- predict(m4, newdata = pred_map, type = "response", se.fit = F)
    heat_dataLuderick$Southeast.Winds[Nn] <- pred_map$X135_degree_winds.standardised[1]
    heat_dataLuderick$Northeast.Winds[Nn] <- pred_map$X45_degree_winds.standardised[1]
    heat_dataLuderick$Abundance[Nn] <- PredX#$fit
    #print(paste("This is line ", Nn, " out of 6561"))
    Nn <- Nn + 1
  }
}

pL <- ggplot(heat_dataLuderick, aes(x = Southeast.Winds,y = Northeast.Winds)) + geom_tile(aes(fill = Abundance)) +
  geom_contour(col="white", aes(z = Abundance)) +#, binwidth = 0.002
  scale_x_continuous(expand = c(0,0)) + 
  scale_y_continuous(expand = c(0,0)) +
  #scale_fill_gradient(low = "blue", high = "red") + 
  theme_classic() + 
  viridis::scale_fill_viridis(option = "magma", name="Predicted Catch") + # or geom_raster()
  xlab("Downwelling \nFavourable Winds") + ylab("Upwelling \nFavourable Winds") +
  theme(axis.title.x = element_text(face="bold", colour="black", size = 15),
        axis.text.x  = element_text(colour="black", size = 14), 
        axis.title.y = element_text(face="bold", colour="black", size = 15),
        axis.text.y  = element_text(colour="black", size = 14),
        axis.ticks = element_line(colour="black"),
        legend.title = element_blank(),
        legend.text = element_text(colour="black", size=10),
        legend.position = "bottom") 

pL

write.csv(heat_dataLuderick, "../Data/Luderick heamap prediction data.csv", row.names = F)

```


##Now Flathead##
Prepare Data
```{r}
flathead <- subset(my.df, Species == "Flathead")
```

Model
```{r}
m5 <- glmmTMB(Catch ~ poly(X135_degree_winds.standardised, degree = 2) + 
       poly(X45_degree_winds.standardised, degree = 2) +
       X135_degree_winds.standardised:X45_degree_winds.standardised+
        Estuary_Type *Drought_Months + (1|Estuary) , Gamma(link="log"),
       data = flathead, offset = log10(Effort_days))
performance::r2(m5) # 0.127
AIC(m5) # 64.26
```

Check assumptions
```{r}
simulationOutput <- simulateResiduals(fittedModel = m5, n = 250)
plot(simulationOutput)

# histograms
hist(simulationOutput$fittedResiduals)
```

```{r}
#png("../plots/Model checks/Flathead model 1.png", width = 21, height = 14.8, units = "cm", res = 600)
#plot(m5)
#dev.off()

#png("../plots/Model checks/Flathead model 2.png", width = 21, height = 14.8, units = "cm", res = 600)
#hist(resid(m5))
#dev.off()

#png("../plots/Model checks/Flathead model 3.png", width = 21, height = 14.8, units = "cm", res = 600)
#lattice::qqmath(m5)
#dev.off()
```


Check significance
```{r}
car::Anova(m5)
summary(m5)
flathead_Summary <- broom.mixed::tidy(m5)
flathead_Summary
write.csv(flathead_Summary, "../Data/Flathead Summary Table.csv", row.names = F)
```
Therefore wind is not important for flathead?

```{r}
plot(ggeffect(m5, terms = "X45_degree_winds.standardised [all]"))
plot(ggeffect(m5, terms = "X135_degree_winds.standardised [all]"))
plot(ggeffect(m5, terms = "Drought_Months [all]"))
```


```{r}
nums <- seq(-2,2, by = 0.05)
heat_dataFlathead <- data.frame("X135_degree_winds.standardised" = rep(0,81*81), # makes empty dataframe ready for values
                         "X45_degree_winds.standardised" =  rep(0,81*81), 
                         "Catch" =  rep(0,81*81))
Nn <- 1
# loop for NE
for (i in 1:length(nums)){
  for (j in 1:length(nums)){
    pred_map <- data.frame("X45_degree_winds.standardised" = nums[i],
                           "X135_degree_winds.standardised" = nums[j],
                           "Drought_Months" = mean(my.df$Drought_Months),
                           "Estuary_Type" = "Drowned River Valley",
                           "Estuary" = "Hawkesbury River",
                           "Effort_days" = mean(my.df$Effort_days))
    PredX <- predict(m5, newdata = pred_map, type = "response", se.fit = F)
    heat_dataFlathead$Southeast.Winds[Nn] <- pred_map$X135_degree_winds.standardised[1]
    heat_dataFlathead$Northeast.Winds[Nn] <- pred_map$X45_degree_winds.standardised[1]
    heat_dataFlathead$Abundance[Nn] <- PredX#$fit
    #print(paste("This is line ", Nn, " out of 6561"))
    Nn <- Nn + 1
  }
}

pF <- ggplot(heat_dataFlathead, aes(x = Southeast.Winds,y = Northeast.Winds)) + geom_tile(aes(fill = Abundance)) +
  geom_contour(col="white", aes(z = Abundance)) +#, binwidth = 0.002
  scale_x_continuous(expand = c(0,0)) + 
  scale_y_continuous(expand = c(0,0)) +
  #scale_fill_gradient(low = "blue", high = "red") + 
  theme_classic() + 
  viridis::scale_fill_viridis(option = "magma", name="Predicted Catch") + # or geom_raster()
  xlab("Downwelling \nFavourable Winds") + ylab("Upwelling \nFavourable Winds") +
  theme(axis.title.x = element_text(face="bold", colour="black", size = 15),
        axis.text.x  = element_text(colour="black", size = 14), 
        axis.title.y = element_text(face="bold", colour="black", size = 15),
        axis.text.y  = element_text(colour="black", size = 14),
        axis.ticks = element_line(colour="black"),
        legend.title = element_blank(),
        legend.text = element_text(colour="black", size=10),
        legend.position = "bottom") 

pF

write.csv(heat_dataFlathead, "../Data/Flathead heamap prediction data.csv", row.names = F)

```